supplementary material for "manifold fitting by ridge estimation: a local kernel density estimation approach"

### 2020-12-15 Ridge_Estimation_main/Ridge_LKDE supplementary.tex
zzh

%% Packages
\RequirePackage{amsthm,amsmath,amsfonts,amssymb,multirow,bbm}
%\RequirePackage[numbers]{natbib}
\RequirePackage[authoryear]{natbib} %% uncomment this for author-year bibliography
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
\RequirePackage{graphicx,graphics,epstopdf}
\RequirePackage{soul}
\newcommand{\Yao}[1]{{\textcolor{red}{[Yao: #1]}}}% added by Yao 10/15/2020

@@

\begin{frontmatter}
\title{supplementary material for "manifold fitting by ridge estimation: a subspace-constrained approach"}
%\title{A sample article title with some additional note\thanksref{t1}}
\runtitle{Manifold fitting by ridge estimation}
%\thankstext{T1}{A sample additional note to the title.}

@@

\begin{proof}\label{Ridge Derivative Lemma}
 For two ridges $R_1, R_2$, we have two density functions $p_1(x)$ and $p_2(x)$ such that the points on each ridge satisfy the solution of
 $\Pi_{H_1}(x) g_1(x) = 0$ 
 and $\Pi_{H_2}(x) g_2(x) = 0$ respectively. For any starting point $x_a \in R_1$, we can build a unit speed curve $\gamma(s)$ derived from the gradient and Hessian of $p_2(x)$ as
 \begin{gather*}
 \gamma_2(0) = x_a \in R_1,\\
 \gamma_2(t_0) = x_b \in R_2,\\
 \gamma'_2(s) = \frac{\Pi_{H_2}(\gamma(s))g_2(\gamma(s))}{\|\Pi_{H_2}(\gamma(s))g_2(\gamma(s))\|_2}.
 \end{gather*}
Note that the curve $\gamma(t)$ connect $x_a$ with $R_2$ by $x_b$. Define the univariate function $\xi(s)$ as
  \[
  \xi_2(s) = p_2(\gamma_2(t_0))-p_2(\gamma_2(s)), \quad 0<s<t_0.
  \]
Through a simple computation, we know 
 \[
 \xi'_2(s)=-\langle  g_2(\gamma_2(s)), \gamma'_2(s) \rangle =- \|\Pi_{H_2}(\gamma_2(s))g_2(\gamma_2(s))\|_2, \quad \xi'_2(t_0) = 0.
 \]
 %\[
 %\xi''(s) = \frac{\langle L_{\gamma'(s)}(\gamma(s)) g(\gamma(s)), L(\gamma(s)g(\gamma(s)))\rangle}{\|L(\gamma(s))g(\gamma(s))\|_2}
 %\]
 %with $\gamma(s)=\frac{L(\gamma(s)g(\gamma(s)))}{\|L(\gamma(s)g(\gamma(s)))\|}$
 The distance from $x_a$ to $R_2$ can be bounded by the curve length of $\gamma_2(t)$ which is $t_0$
 \[
 \begin{aligned}
 &d(x_a, R_2) \\
 =& \|x_a-P_{R_2}(x_a)\|_2\\
 \leq& \|x_a-x_b\|_2 \\
 = &\|\gamma_2(t_0)-\gamma_2(0)\|_2\leq t_0.
 \end{aligned}
 \]
Finally, the problem becomes to bound $t_0$. Suppose $\sup_u \xi''_2(u)>\frac{1}{c}$, by the mean-value theorem, we have
 \[
 \begin{aligned}
 t_0 = &\frac{\xi'_2(t_0)-\xi'_2(0)}{\xi''_2(u)} \\
 = &\frac{\|\Pi_{H_2}(\gamma_2(0))g_2(\gamma_2(0))\|_2}{\xi''_2(u)} \\
 \leq & c \|\Pi_{H_2}(\gamma_2(0))g_2(\gamma_2(0))\|_2.
 \end{aligned}
 \]
 Next, we show that $\|\Pi_{H_2}(\gamma_2(0))g_2(\gamma_2(0))\|_2$ is of the same order with an approximation error of $H_2(x)$ and $g_2(x)$:
 \begin{equation}
 \begin{aligned}\label{bound_temp1}
 &\|\Pi_{H_2}(\gamma_2(0))g_2(\gamma_2(0))\|_2\\
 =&  \|\Pi_{H_2}(\gamma_2(0))g_2(\gamma_2(0)) - \Pi_{H_1}(\gamma_2(0))g_1(\gamma_2(0))\|_2
 \end{aligned}
 \end{equation}
 Using the triangle-inequality with respect to the $\|\|_2$ norm, we have \eqref{bound_temp1} is dominated by
 \begin{equation}\label{bound_temp2}
 \begin{aligned}
& \|\Pi_{H_2}(\gamma_2(0))g_2(\gamma_2(0)) -\Pi_{H_1}(\gamma_2(0)){g_2}(\gamma_2(0)) \|_2 +...\\
 & \quad \quad  \quad \quad  \quad \quad + \|\Pi_{H_1}(\gamma_2(0)){g_2}(\gamma_2(0)) - \Pi_{H_1}(\gamma_2(0))g_1(\gamma_2(0))\|_2\\
 \end{aligned}
 \end{equation}
 For any matrix $A$, using the Cauchy-Schwartz inequality on each row of $A$, we will get the result $\|Ax\|_2\leq \|A\|_F\|x\|_2$. Thus, similarly, we have \eqref{bound_temp2} is dominated by
 \[
 \begin{aligned}
 & \|\Pi_{H_2}(\gamma_2(0)) - \Pi_{H_1}(\gamma_2(0))\|_F\|g_2(\gamma_2(0))\|_2 +...\\
 &\quad \quad  \quad \quad  \quad \quad  +\|\Pi_{H_1}(\gamma_2(0))\|_F\|g_2(\gamma_2(0))-g_1(\gamma_2(0))\|_2, \\
 \end{aligned}.
 \]
According to the Davis-Kahan theorem, $\|\Pi_{H_2}(\gamma_2(t))-\Pi_{H_1}(\gamma_2(t))\|_F \leq \beta\|H_2(\gamma_2(t))-H_1(\gamma_2(t))\|_F$. The conclusion is proved!
\end{proof}

@@

\begin{proof}
Suppose the kernel function vanishes at infinity for each dimension, i.e., it satisfies $\lim_{u_s\rightarrow \infty}K(u)=0$ for each dimension. Then, using the integration-by-parts formula, we obtain the expectation of first-order derivatives:
\begin{equation}\label{Expectation}
\begin{aligned}
&{\rm E} (\partial_{x_s} \hat{p}_h(x)) \\
\overset{s.1}{=}& \frac{1}{h^D} \int_{y\in \mathbb{R}^D}{\partial_{x_s}}  K(\frac{x-y}{h}) p(y) dy  \\
\overset{s.2}{=}&\frac{1}{h^{D+1}}\int \partial_{z_s} K(z)|_{z=\frac{x-y}{h}} p(y) dy\\
\overset{s.3}{=}&h^{-1} \int_ {u\in \mathbb{R}^D} \partial_{u_s} K(u) p(x-hu)  d u\\
\overset{s.4}{=}&h^{-1}\int_ {u\in \mathbb{R}^D} K(u) \partial_{u_s} p(x-hu) d u \\
\overset{s.5}{=}& \int_ {u\in \mathbb{R}^D} K(u) \partial_{z_s}p(z)|_{z=x-hu} d u.
\end{aligned}
\end{equation}
%We explain the reason for each steps as: 
The equation $s.1$ is the definition of expectation. The equation $s.2$ is obtained from the derivative of the function composition. The equation $s.3$ is obtained from the formula of integration by changing variables. The equation $s.4$ is obtained from the formula of the integration by partition. The equation $s.5$ is similar with that of equation $s.2$.

For the multivariate function $\partial_{x_s} p(x)$, we have the Taylor expansion of $\partial_{x_s} p(x)$ up to order 2 as
\begin{equation}\label{Taylor}
\begin{aligned}
&\partial_{z_s} p(z)|_{z=x-hu}\\
= &\partial_{x_s} p(x) -  h u^T\nabla \partial_{x_s} p(x) + \frac{1}{2}h^2 u^T H(\partial_{x_s}p(x))u + o(h^2).
\end{aligned}
\end{equation}

Since $u^T \nabla \partial_{x_s} p(x) K(u)$ is an odd function with respect to each variable $u_s$, we have the integration $\int u^T \nabla \partial_{x_s} p(x) K(u) du = 0 $ in a symmetric region.

For the term $u^T H(\partial_{x_s}p(x))u$, we know it is related with the Laplace Beltrami operator of $\Delta(\partial_{x_s}p(x))$ by
\[
\begin{aligned}
\int u^T H(\partial_{x_s}p(x))u K(u) du =& \langle \int uu^TK(u) du, H(\partial_{x_s}p(x))\rangle\\
\overset{s.6}{=}&\frac{\int \|u\|_2^2K(u)du}{D} \langle  I, H(\partial_{x_s}p(x))\rangle\\
=&\frac{\int \|u\|_2^2K(u)du}{D} \Delta(\partial_{x_s}p(x)),
\end{aligned}
\]
where the equation of $s.6$ is obtained from $\|u\|_2^2 = \sum_k u^2_k$, and
\[
\int u_k u_s K(u)du=0 \quad k\neq s,
\] because of symmetric domain of integration and the independence  for each of the dimensions.

Combining the above results, we know the bias
\begin{equation}\label{BiasResult}
|{\rm E}(\partial_{x_s} \hat{p}_h(x)) - \partial_{x_s}p(x)|  = \frac{|\Delta(\partial_{x_s} p(x))|}{2D} h^2 \int \|u\|_2^2 K(u) du+o(h^2),
\end{equation}
where $\Delta(\partial_{x_s} p(x))$ is the Laplace-Beltrami operator of $\partial_{x_s} p(x)$, which is also the summation of the diagonal elements of the Hessian matrix $H(\partial_{x_s}p(x))$. Similarly, repeating the same procedure as \eqref{Expectation}\eqref{Taylor}, we have the second-order bias as
%where $\lambda_s(x)$ is the largest eigenvalue of the Hessian matrix $H(\partial_{x_s}p(x))$. 
\begin{equation}\label{order2}
|{\rm E}( \partial_{x_s} \partial_{x_t}   \hat{p}_h(x)) -  \partial_{x_s} \partial_{x_t} p(x)| = \frac{|\Delta(\partial_{x_s}\partial_{x_t} p(x))|}{2D} h^2 \int \|u\|_2^2 K(u) du+o(h^2).
\end{equation}
The same with \eqref{BiasResult}, $\Delta(\partial_{x_s}\partial_{x_t} p(x))$ is the Laplace-Beltrami operator of $\partial_{x_s}\partial_{x_t} p(x)$ which is also the summation of the eigenvalues of the matrix $M_{s,t}$ whose $i,j$-th element is $\frac{\partial^4}{\partial x_s\partial x_t \partial x_i \partial x_j} p(x)$.%, i.e., $\lambda_{st}(x)= \max_k \lambda_k( M_{st}(x))$.
\end{proof}
\subsection{Derivatives' Variance Bound}\label{variance_proof}
\begin{theorem}
The variance of the first and second order derivatives for $\hat{p}_h(x)$ has a bound as 
\begin{equation*}\label{VarResult}
\begin{aligned}
&{\rm E} |\partial_{x_s} \hat{p}_h(x)-{\rm E}(\partial_{x_s} \hat{p}_h(x))| = \sqrt{\frac{\phi_s(x)}{n h^{D+2}}}+O(\frac{1}{n^{1/2}h^{(D+1)/2}}),\\
&{\rm E} | \partial_{x_s}\partial_{x_t} \hat{p}_h(x) -{\rm E}(\partial_{x_s}\partial_{x_t} \hat{p}_h(x))| = \sqrt{\frac{\phi_{s,t}(x)}{nh^{D+4}}}+O(\frac{1}{n^{1/2}h^{(D+3)/2}}).
\end{aligned}
\end{equation*}
%where $M(u) = \partial_{u_s}K(u)$ and $N(u) = \partial_{u_t}\partial_{u_s}K(u)$, respectively.
\end{theorem}

\begin{proof}
Because of the i.i.d. assumption and the characters of the variance, the first-order derivative yields
\[
\begin{aligned}
 &{\rm Var} (\partial_{x_s} \hat{p}_h(x))  \\
 \overset{s.7}{=} &{\rm Var} (\frac{1}{n h^D}\sum_k \partial_{x_s}(K(\frac{x-y_k}{h})))\\
 \overset{s.8} = &\frac{1}{n h^{2D}} {\rm Var}(  \partial_{x_s} K(\frac{x-y}{h}))))\\
 \overset{s.9} = & \frac{1}{n h^{2D+2}} {\rm Var} (\partial_ {u_s}  K(u)|_{u=\frac{x-y}{h}}).%= \frac{1}{n h^{2d+4}} (E_y({k^{''}}^2_{rs}(\frac{x-y}{h}))- E_y^2(k^{''}_{rs}(\frac{x-y}{h}))
\end{aligned}
\]
Similarly as the process derived in the bias, equation $s.7$ is the definition of variance, equation $s.8$ is obtained from the independence of the samples of $y_k$ and equation $s.9$ is because of derivative for the composite functions.

@@

In addition, denote $M(\frac{x-y}{h}) = \partial_ {u_s}  K(u)|_{u=\frac{x-y}{h}}$, the variance will lead to

@@

 &{\rm Var} (\partial_{x_s} \hat{p}_h(x))\\
  = &\frac{1}{nh^{2D+2}}({\rm E}_y (M^2(\frac{x-y}{h}))-{\rm E}^2_y(M(\frac{x-y}{h}))).

@@

= &h^{D+1} ( {\rm E}(\partial_{x_s} \hat{p}_h(x))\\
\leq &h^{D+1} (\partial_{x_s} p(x)+\frac{\Delta(\partial_{x_s}p(x))}{2D} h^2 \int \|u\|^2 K(u) du+o(h^2)).

@@

&{\rm E}_y(M^2(\frac{x-y}{h})) \\
=& \frac{1}{h^D} \int M^2(u) p(x-uh) du \\
= &\frac{1}{h^D}(p(x)\int M^2(u)du+O(h)).

@@

Combining the results in \eqref{EM} and \eqref{part1} we have the order of the variance is

@@

=& \frac{1}{n h^{2D+2}}({\rm E}_yM^2(\frac{x-y}{h}))-{\rm E}^2_y(M(\frac{x-y}{h})) \\
=& \frac{1}{n h^{D+2}} (p(x)\int M^2(u)du +O(h)).

@@

Because the square-root function is concave, we use Jensen's inequality to show that ${\rm E} |\partial_{x_s} \hat{p}_h(x)-{\rm E}(\partial_{x_s} \hat{p}_h(x))|$ is dominated by the square root of the variance as

@@

 & {\rm E}|\partial_{x_s} \hat{p}_h(x)-{\rm E}(\partial_{x_s} \hat{p}_h(x))|\\
\leq &\sqrt{{\rm E}(\partial_{x_s} \hat{p}_h(x)-{\rm E}(\partial_{x_s} \hat{p}_h(x)))^2}\\
 = & \sqrt{{\rm Var}(\partial_{x_s}\hat{p}_h(x))} .

@@

%\begin{equation}\label{Jensen}
%\begin{aligned}
%  & \sqrt{{\rm Var}(\partial_{x_s}\hat{p}_h(x))} \\
%=& \sqrt{{\rm E}(\partial_{x_s} \hat{p}_h(x)-{\rm E}(\partial_{x_s} \hat{p}_h(x)))^2}\\
%\geq &{\rm E} |\partial_{x_s} \hat{p}_h(x)-{\rm E}(\partial_{x_s} \hat{p}_h(x))|.
%\end{aligned}

@@

&{\rm E} |\partial_{x_s} \hat{p}_h(x)-{\rm E}(\partial_{x_s} \hat{p}_h(x))| \\
\leq &\sqrt{\frac{p(x)\int M^2(u)du}{n h^{D+2}}}+O(\frac{1}{n^{1/2}h^{(D+1)/2}}).

@@

&{\rm E} | \partial_{x_s}\partial_{x_t} \hat{p}_h(x) -{\rm E}(\partial_{x_s}\partial_{x_t} \hat{p}_h(x))| \\
\leq & \sqrt{\frac{p(x)\int N^2(u)du}{nh^{D+4}}}+O(\frac{1}{n^{1/2}h^{(D+3)/2}}),

@@

&\partial_{z_s} p(z)|_{z=x-hu}
= \partial_{x_s} p(x) -  h u^T\nabla \partial_{x_s} p(x) + \frac{1}{2}h^2 u^T H(\partial_{x_s}p(x))(x)u + o(h^2).

@@

&{\rm E} (\partial_{x_s} \hat{p}_{r,h}(x))  \\
=& \partial_{x_s} p(x) \int_ {u\in \mathbb{R}^D} K_r(u) du+... \\
+& \frac{\Delta(\partial_{x_s}p(x))}{2D} h^2 \int_{\|u\|\leq r/h } \|u\|_2^2 K(u) du + o(h^2).

@@

= & -\partial_{x_s} p(x) \int_{\|u\|\geq r/h} K(u) du  +...\\
+& \frac{\Delta(\partial_{x_s} p(x))}{2D} h^2 \int_{\|u\|\leq r/h } \|u\|_2^2 K(u) du .

@@

\leq &|\partial_{x_s} p(x)| \int_{\|u\|\geq r/h} K(u) du  + ...\\
+&\frac{|\Delta(\partial_{x_s} p(x))|}{2D} h^2 \int_{\|u\|\leq r/h } \|u\|_2^2 K(u) du .

@@

&\frac{|\Delta(\partial_{x_s} p(x))|}{2} h^2 \int_{\|u\|> r /h} \|u\|_2^2 K(u) du\\
 >& |\partial_{x_s} p(x)| \int_{\|u\|> r/h} K(u) du.

@@

\section{}
\subsection{Eigenspace Differences betweeen $C_r(x)$ and $J_r(x)$}
\begin{theorem}
If $\|c_r(x)-x\|_2^2< \lambda_d(C_r(x)))$, the eigenspaces corresponding to the top $d$ eigenvalues of $C_r(x)$ and $J_r(x)$ coincide, i.e., the distance 
%\footnote{
%The distance between two subspace ${\cal V}$ and ${\cal U} $ is defined as the operator norm of the error of two projection matrices, i.e., $D({\cal V},{\cal U}) = \|P_{\cal V}-P_{\cal U}\|_2$
%}
\[
D({\cal V}_d (C_r(x)), {\cal V}_d (J_r(x)))=0,
\]
Otherwise, if $\|c_r(x)-x\|_2^2\geq \lambda_d(C_r(x)))$, then 
$
D({\cal V}_d (C_r(x)),{\cal V}_d (J_r(x)))=1.
$
\end{theorem}
\begin{proof}
%To simplify the analysis, we assume the orthogonality of $c_r(x)-x$ and the space spanned by the top $d$ eigenspace of $\sum_i w_h(x, x_i) (x_i-c_r(x)) (x_i-c_r(x))^T$.

@@

\begin{figure}[t] %  figure placement: here, top, bottom, or page
%\includegraphics[width=0.32\linewidth]{../figures/demo1.eps} 
%\hspace{-4mm}\includegraphics[width=0.32\linewidth]{../figures/demo2.eps} 
%\hspace{-4mm}\includegraphics[width=0.32\linewidth]{../figures/demo3.eps} 
\includegraphics[width=\linewidth]{demo123.eps} 
%\setcaptionwidth{6in}
\caption{The process of $J_r(x)$'s eigenspace's variation with $x$ approaching the manifold }
\label{Shifting Eigenvectors}
\end{figure}

@@

%\bibliographystyle{imsart-number}
\bibliographystyle{imsart-nameyear}
\bibliography{bibfile}

>>>>

%% Packages
\RequirePackage{amsthm,amsmath,amsfonts,amssymb,multirow,bbm}
%\RequirePackage[numbers]{natbib}
%\RequirePackage[authoryear]{natbib} %% uncomment this for author-year bibliography
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
\RequirePackage{graphicx,graphics,epstopdf}
\RequirePackage{soul}
\newcommand{\Yao}[1]{{\textcolor{red}{[Yao: #1]}}}% added by Yao 10/15/2020

@@

\begin{frontmatter}
\title{supplementary material for "manifold fitting by ridge estimation: a local kernel density estimation approach"}
%\title{A sample article title with some additional note\thanksref{t1}}
\runtitle{Manifold fitting by ridge estimation}
%\thankstext{T1}{A sample additional note to the title.}

@@

\begin{proof}\label{Ridge Derivative Lemma}
 For two ridges $R_1, R_2$, we have two density functions $p_1(x)$ and $p_2(x)$ such that the points on each ridge satisfy the solution of
 $\Pi_{H_1}(x) g_1(x) = 0$ 
 and $\Pi_{H_2}(x) g_2(x) = 0$ respectively. For any starting point $x_a \in R_1$, we can build a unit speed curve $\gamma(s)$ derived from the gradient and Hessian of $p_2(x)$ as
 \[
 \gamma_2(0) = x_a \in R_1, \quad \gamma_2(t_0) = x_b \in R_2, \quad \gamma'_2(s) = \frac{\Pi_{H_2}(\gamma(s))g_2(\gamma(s))}{\|\Pi_{H_2}(\gamma(s))g_2(\gamma(s))\|_2}.
 \]
Note that the curve $\gamma(t)$ connect $x_a$ with $R_2$ by $x_b$. Define the univariate function $\xi(s)$ as
  \[
  \xi_2(s) = p_2(\gamma_2(t_0))-p_2(\gamma_2(s)), \quad 0<s<t_0.
  \]
Through a simple computation, we know 
 \[
 \xi'_2(s)=-\langle  g_2(\gamma_2(s)), \gamma'_2(s) \rangle =- \|\Pi_{H_2}(\gamma_2(s))g_2(\gamma_2(s))\|_2, \quad \xi'_2(t_0) = 0.
 \]
 %\[
 %\xi''(s) = \frac{\langle L_{\gamma'(s)}(\gamma(s)) g(\gamma(s)), L(\gamma(s)g(\gamma(s)))\rangle}{\|L(\gamma(s))g(\gamma(s))\|_2}
 %\]
 %with $\gamma(s)=\frac{L(\gamma(s)g(\gamma(s)))}{\|L(\gamma(s)g(\gamma(s)))\|}$
 The distance from $x_a$ to $R_2$ can be bounded by the curve length of $\gamma_2(t)$ which is $t_0$
 \[
 d(x_a, R_2) = \|x_a-P_{R_2}(x_a)\|_2\leq \|x_a-x_b\|_2 = \|\gamma_2(t_0)-\gamma_2(0)\|_2\leq t_0.
 \]
Finally, the problem becomes to bound $t_0$. Suppose $\sup_u \xi''_2(u)>\frac{1}{c}$, by the mean-value theorem, we have
 \[
 t_0 = \frac{\xi'_2(t_0)-\xi'_2(0)}{\xi''_2(u)} = \frac{\|\Pi_{H_2}(\gamma_2(0))g_2(\gamma_2(0))\|_2}{\xi''_2(u)} \leq c \|\Pi_{H_2}(\gamma_2(0))g_2(\gamma_2(0))\|_2.
 \]
 Next, we show that $\|\Pi_{H_2}(\gamma_2(0))g_2(\gamma_2(0))\|_2$ is of the same order with an approximation error of $H_2(x)$ and $g_2(x)$:
 \[
 \begin{aligned}
 \|\Pi_{H_2}(\gamma_2(0))g_2(\gamma_2(0))\|_2=&  \|\Pi_{H_2}(\gamma_2(0))g_2(\gamma_2(0)) - \Pi_{H_1}(\gamma_2(0))g_1(\gamma_2(0))\|_2\\
 \leq & \|\Pi_{H_2}(\gamma_2(0))g_2(\gamma_2(0)) -\Pi_{H_1}(\gamma_2(0)){g_2}(\gamma_2(0)) \|_2 +...\\
 & + \|\Pi_{H_1}(\gamma_2(0)){g_2}(\gamma_2(0)) - \Pi_{H_1}(\gamma_2(0))g_1(\gamma_2(0))\|_2\\
 \leq & \|\Pi_{H_2}(\gamma_2(0)) - \Pi_{H_1}(\gamma_2(0))\|_F\|g_2(\gamma_2(0))\|_2 +...\\
 &+\|\Pi_{H_1}(\gamma_2(0))\|_F\|g_2(\gamma_2(0))-g_1(\gamma_2(0))\|_2, \\
 \end{aligned}.
 \]
 where the last inequality is obtained by applying the Cauchy-Schwartz inequality on each row of $A$, to get the result $\|Ax\|_2\leq \|A\|_F\|x\|_2$. According to the Davis-Kahan theorem, $\|\Pi_{H_2}(\gamma_2(t))-\Pi_{H_1}(\gamma_2(t))\|_F \leq \beta\|H_2(\gamma_2(t))-H_1(\gamma_2(t))\|_F$. The conclusion is proved!
\end{proof}

@@

\begin{proof}
Suppose the kernel function vanishes at infinity for each dimension, i.e., it satisfies $\lim_{u_s\rightarrow \infty}K(u)=0$ for each dimension. Then, using the integration-by-parts formula, we obtain the expectation of first-order derivatives:
\begin{equation}\label{Expectation}
\begin{aligned}
{\rm E} (\partial_{x_s} \hat{p}_h(x)) &= \frac{1}{h^D} \int_{y\in \mathbb{R}^D}{\partial_{x_s}}  K(\frac{x-y}{h}) p(y) dy  \\
&=\frac{1}{h^{D+1}}\int \partial_{z_s} K(z)|_{z=\frac{x-y}{h}} p(y) dy=h^{-1} \int_ {u\in \mathbb{R}^D} \partial_{u_s} K(u) p(x-hu)  d u\\
&=h^{-1}\int_ {u\in \mathbb{R}^D} K(u) \partial_{u_s} p(x-hu) d u = \int_ {u\in \mathbb{R}^D} K(u) \partial_{z_s}p(z)|_{z=x-hu} d u.
\end{aligned}
\end{equation}
For the multivariate function $\partial_{x_s} p(x)$, we have the Taylor expansion up to order 2 as
\begin{equation}\label{Taylor}
\partial_{z_s} p(z)|_{z=x-hu}= \partial_{x_s} p(x) -  h u^T\nabla \partial_{x_s} p(x) + \frac{1}{2}h^2 u^T H(\partial_{x_s}p(x))u + o(h^2).
\end{equation}
Since $u^T \nabla \partial_{x_s} p(x) K(u)$ is an odd function with respect to each variable $u_s$, we have the integration $\int u^T \nabla \partial_{x_s} p(x) K(u) du = 0 $ in a symmetric region.

For the term $u^T H(\partial_{x_s}p(x))u$, we know it is related with the Laplace Beltrami operator of $\Delta(\partial_{x_s}p(x))$ by
\[
\begin{aligned}
\int u^T H(\partial_{x_s}p(x))u K(u) du =& \langle \int uu^TK(u) du, H(\partial_{x_s}p(x))\rangle\\
=&\frac{\int \|u\|_2^2K(u)du}{D} \langle  I, H(\partial_{x_s}p(x))\rangle\\
=&\frac{\int \|u\|_2^2K(u)du}{D} \Delta(\partial_{x_s}p(x))
\end{aligned}
\]
Merging the above results, we know the bias
\begin{equation}\label{BiasResult}
|{\rm E}(\partial_{x_s} \hat{p}_h(x)) - \partial_{x_s}p(x)|  = \frac{|\Delta(\partial_{x_s} p(x))|}{2D} h^2 \int \|u\|_2^2 K(u) du+o(h^2),
\end{equation}
where $\Delta(\partial_{x_s} p(x))$ is the Laplace-Beltrami operator of $\partial_{x_s} p(x)$, which is also the summation of the diagonal elements of the Hessian matrix $H(\partial_{x_s}p(x))$. Similarly, repeating the same procedure as \eqref{Expectation}\eqref{Taylor}, we have the second-order bias as
%where $\lambda_s(x)$ is the largest eigenvalue of the Hessian matrix $H(\partial_{x_s}p(x))$. 
\begin{equation}\label{order2}
|{\rm E}( \partial_{x_s} \partial_{x_t}   \hat{p}_h(x)) -  \partial_{x_s} \partial_{x_t} p(x)| = \frac{|\Delta(\partial_{x_s}\partial_{x_t} p(x))|}{2D} h^2 \int \|u\|_2^2 K(u) du+o(h^2).
\end{equation}
The same with \eqref{BiasResult}, $\Delta(\partial_{x_s}\partial_{x_t} p(x))$ is the Laplace-Beltrami operator of $\partial_{x_s}\partial_{x_t} p(x)$ which is also the summation of the eigenvalues of the matrix $M_{s,t}$ whose $i,j$-th element is $\frac{\partial^4}{\partial x_s\partial x_t \partial x_i \partial x_j} p(x)$.%, i.e., $\lambda_{st}(x)= \max_k \lambda_k( M_{st}(x))$.
\end{proof}
\subsection{Derivatives' Variance Bound}\label{variance_proof}
\begin{theorem}
The variance of the first and second order derivatives for $\hat{p}_h(x)$ has a bound as 
\begin{equation*}\label{VarResult}
\begin{aligned}
&{\rm E} |\partial_{x_s} \hat{p}_h(x)-{\rm E}(\partial_{x_s} \hat{p}_h(x))| = \sqrt{\frac{\phi_s(x)}{n h^{D+2}}}+O(\frac{1}{n^{1/2}h^{(D+1)/2}}),\\
&{\rm E} | \partial_{x_s}\partial_{x_t} \hat{p}_h(x) -{\rm E}(\partial_{x_s}\partial_{x_t} \hat{p}_h(x))| = \sqrt{\frac{\phi_{s,t}(x)}{nh^{D+4}}}+O(\frac{1}{n^{1/2}h^{(D+3)/2}}).
\end{aligned}
\end{equation*}
%where $M(u) = \partial_{u_s}K(u)$ and $N(u) = \partial_{u_t}\partial_{u_s}K(u)$, respectively.
\end{theorem}
Because of the i.i.d. assumption and the characters of the variance, the first-order derivative yields
 &{\rm Var} (\partial_{x_s} \hat{p}_h(x))  = {\rm Var} (\frac{1}{n h^D}\sum_k \partial_{x_s}(K(\frac{x-y_k}{h})))\\
  = &\frac{1}{n h^{2D}} {\rm Var}(  \partial_{x_s} K(\frac{x-y}{h}))))=  \frac{1}{n h^{2D+2}} {\rm Var} (\partial_ {u_s}  K(u)|_{u=\frac{x-y}{h}}).%= \frac{1}{n h^{2d+4}} (E_y({k^{''}}^2_{rs}(\frac{x-y}{h}))- E_y^2(k^{''}_{rs}(\frac{x-y}{h}))

@@

In addition, let $M(\frac{x-y}{h}) = \partial_ {u_s}  K(u)|_{u=\frac{x-y}{h}}$, which will lead to

@@

 {\rm Var} (\partial_{x_s} \hat{p}_h(x)) = \frac{1}{nh^{2D+2}}({\rm E}_y (M^2(\frac{x-y}{h}))-{\rm E}^2_y(M(\frac{x-y}{h}))).

@@

= &h^{D+1} ( {\rm E}(\partial_{x_s} \hat{p}_h(x))\leq h^{D+1} (\partial_{x_s} p(x)+\frac{\Delta(\partial_{x_s}p(x))}{2D} h^2 \int \|u\|^2 K(u) du+o(h^2)).

@@

{\rm E}_y(M^2(\frac{x-y}{h})) = \frac{1}{h^D} \int M^2(u) p(x-uh) du = \frac{1}{h^D}(p(x)\int M^2(u)du+O(h)).

@@

Using \eqref{EM},\eqref{part1} we have

@@

=& \frac{1}{n h^{2D+2}}({\rm E}_yM^2(\frac{x-y}{h}))-{\rm E}^2_y(M(\frac{x-y}{h})) = \frac{1}{n h^{D+2}} (p(x)\int M^2(u)du +O(h)).

@@

Because the square-root function is concave, we use Jensen's inequality to determine that

@@

\sqrt{{\rm Var}(\partial_{x_s}\hat{p}_h(x))} = \sqrt{{\rm E}(\partial_{x_s} \hat{p}_h(x)-{\rm E}(\partial_{x_s} \hat{p}_h(x)))^2}\geq {\rm E} |\partial_{x_s} \hat{p}_h(x)-{\rm E}(\partial_{x_s} \hat{p}_h(x))|.

@@

@@

{\rm E} |\partial_{x_s} \hat{p}_h(x)-{\rm E}(\partial_{x_s} \hat{p}_h(x))| \leq \sqrt{\frac{p(x)\int M^2(u)du}{n h^{D+2}}}+O(\frac{1}{n^{1/2}h^{(D+1)/2}}).

@@

{\rm E} | \partial_{x_s}\partial_{x_t} \hat{p}_h(x) -{\rm E}(\partial_{x_s}\partial_{x_t} \hat{p}_h(x))| \leq \sqrt{\frac{p(x)\int N^2(u)du}{nh^{D+4}}}+O(\frac{1}{n^{1/2}h^{(D+3)/2}}),

@@

&\partial_{z_s} p(z)|_{z=x-hu}= \partial_{x_s} p(x) -  h u^T\nabla \partial_{x_s} p(x) + \frac{1}{2}h^2 u^T H(\partial_{x_s}p(x))(x)u + o(h^2).

@@

{\rm E} (\partial_{x_s} \hat{p}_{r,h}(x))  = \partial_{x_s} p(x) \int_ {u\in \mathbb{R}^D} K_r(u) du + \frac{\Delta(\partial_{x_s}p(x))}{2D} h^2 \int_{\|u\|\leq r/h } \|u\|_2^2 K(u) du + o(h^2).

@@

= &
-\partial_{x_s} p(x) \int_{\|u\|\geq r/h} K(u) du  + \frac{\Delta(\partial_{x_s} p(x))}{2D} h^2 \int_{\|u\|\leq r/h } \|u\|_2^2 K(u) du .

@@

\leq &
|\partial_{x_s} p(x)| \int_{\|u\|\geq r/h} K(u) du  + \frac{|\Delta(\partial_{x_s} p(x))|}{2D} h^2 \int_{\|u\|\leq r/h } \|u\|_2^2 K(u) du .

@@

\frac{|\Delta(\partial_{x_s} p(x))|}{2} h^2 \int_{\|u\|> r /h} \|u\|_2^2 K(u) du > |\partial_{x_s} p(x)| \int_{\|u\|> r/h} K(u) du.

@@

\section{}
\subsection{Eigenspace Differences betweeen $C_r(x)$ and $J_r(x)$}
\begin{theorem}
If $\|c_r(x)-x\|_2^2< \lambda_d(C_r(x)))$, the eigenspaces corresponding to the top $d$ eigenvalues of $C_r(x)$ and $J_r(x)$ coincide, i.e., the distance \footnote{
The distance between two subspace ${\cal V}$ and ${\cal U} $ is defined as the operator norm of the error of two projection matrices, i.e., $D({\cal V},{\cal U}) = \|P_{\cal V}-P_{\cal U}\|_2$
}
\[
D({\cal V}_d (C_r(x)), {\cal V}_d (J_r(x)))=0,
\]
Otherwise, if $\|c_r(x)-x\|_2^2\geq \lambda_d(C_r(x)))$, then 
$
D({\cal V}_d (C_r(x)),{\cal V}_d (J_r(x)))=1.
$
\end{theorem}
\begin{proof}
%To simplify the analysis, we assume the orthogonality of $c_r(x)-x$ and the space spanned by the top $d$ eigenspace of $\sum_i w_h(x, x_i) (x_i-c_r(x)) (x_i-c_r(x))^T$.

@@

\begin{figure}[t] %  figure placement: here, top, bottom, or page
%\includegraphics[width=0.32\linewidth]{../figures/demo1.eps} 
%\hspace{-4mm}\includegraphics[width=0.32\linewidth]{../figures/demo2.eps} 
%\hspace{-4mm}\includegraphics[width=0.32\linewidth]{../figures/demo3.eps} 
\includegraphics[width=\linewidth]{demo123.eps} 
%\setcaptionwidth{6in}
\caption{The process of $J(x)$'s eigenspace's variation with $x$ approaching the manifold }
\label{Shifting Eigenvectors}
\end{figure}

@@

\bibliographystyle{imsart-number}
%\bibliographystyle{imsart-nameyear}
\bibliography{bibfile}
